A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-28 paper.tex
Work in progress
Update

One strategic difference in our algorithm implementation is the reproduction
process, which is flexible to work in parallel with multiple couple selection
methods, for example, tournament selection, random selection (closed
reproduction), and couple match by creating a new mating individual (open
reproduction). We use many combinations of the containerized processes, up to
the minimum number required to obtain good results. Figure 4 shows a comparison
of only two alternatives for the implementation of the algorithm. Our
experimentation started with a configuration of ten processes and ended in
five, shown on the left and right sides of figure 4, respectively.

>>>>

One strategic difference in our algorithm implementation is the reproduction
process, which is flexible to work in parallel with multiple couple selection
methods, for example, tournament selection, random selection (closed
reproduction), and couple match by creating a new mating individual (open
reproduction). We use many combinations of the containerized processes, up to
the minimum number required to obtain good results. Figure 5 shows a comparison
of only two alternatives for the implementation of the algorithm. Our
experimentation started with a configuration of ten processes and ended in
five, shown on the left and right sides of figure 5, respectively.
